Spotify Data

### 2024-10-10 paper/paper.qmd
Update

The dataset was accessed using the `spotifyr` package (@spotifyr). For the analysis, the R programming language was employed (@r), utilizing the `tidyverse` (@tidyverse) package for data cleaning, transformation, visualization, and the `here` package (@here) accessing the data in this analysis. Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package (@tidyverse).

@@

>>>>

The dataset was accessed using the `spotifyr` package (@spotifyr). For the analysis, the R programming language was employed (@r), utilizing the `tidyverse` (@tidyverse) package for data cleaning, transformation, visualization, the `knitr` package to visualize the data, and the `here` package (@here) accessing the data in this analysis. Afterward, the cleaned dataset was processed and tested using additional functions from the `tidyverse` package (@tidyverse).

@@

This (@tbl-data) is the preview of the dataset.

```{r}
#| label: tbl-data
#| tbl-cap: Preview of Data
#| echo: false
#| warning: false
#| message: false

kable(head(data), format = "markdown")
```
